Automating Verification of MPC Security

### 2023-06-08 popl24/minicat.tex
checkpoint

Here we introduce some examples to illustrate $\minifed$ and how it
can be used to model secure communication protocols for values in the
binary field. Most of these are translations (into $\minifed$) of
object examples in previous related work \cite{XXX}. We will return to
these as running examples throughout the paper to illustrate various
concepts and advantages of our methods.
\begin{example}[One-Time Pad]
  \label{example-otp}
As observed in \cite{XXX} and elsewhere, coin flips with $\exor$ can
be used to model one-time pad encryption in the binary field. On the
basis of this we can model secure communication between over an
insecure channel using symmetric key encryption. In the following
program, we assume $H = \{ 1,2 \}$ and $C = \{ 0 \}$. Client 1 first
shares the randomly generated ``key'' $\fx{1}{0}$ with client 2
through view $\view{2}{0}$. Then, client 1 encrypts its secret
$\sx{1}{0}$ and sends it to party 0, which relays the ciphertext in
$\vx{0}{0}$ to client 2. Finally, client 2 decrypts the the ciphertext
and stores the plaintext in $\vx{2}{2}$.
\begin{verbatimtab}
v[2,0] := f[1,0];
v[0,0] := f[1,0] xor s[1,0];
v[2,1] := v[0,0];
v[2,2] := v[2,1] xor v[2,0]
\end{verbatimtab}
Intuitively, this protocol is \emph{correct} because $\vx{2}{2}$ is
exactly correlated with the secret $\sx{1}{0}$, and it is
\emph{secure} because the corrupt view $\vx{0}{0}$ in isolation is
probabilistically independent of the secret $\sx{1}{0}$.
\end{example}

\begin{example}[$\lambda_{\mathrm{obliv}}$]
  \label{example-lambda-obliv}
  In \cite{XXX}, Figure 3, two examples are introduced that illustrate
  subtleties of probabilistic programming in
  $\lambda_{\mathrm{obliv}}$, a language for oblivious memory
  management. We consider their translations here where we
  assume $H = \{ 1 \}$ and $C = \{ 0 \}$. First, the following
  examples shows that reuse of coin flips can result in release of
  information, even though flips are chosen from a uniform
  distribution. This is because the adversary can deduce that
  $\secret{1}{s}$ is more likely to be 1 in case their views are the
  same value:
  \begin{verbatimtab}
    v[0,0] := select(s[1,s], flip[1,sx], flip[1,sy]);
    v[0,1] := flip[1,sx] \end{verbatimtab}
  In the next example, since the nested select is more likely to evaluate
  to $1$ than $0$, the adversary can deduce that $\secret{1}{s}$ is
  more likely to be 1 in case $\view{0}{0}$ is 1:
  \begin{verbatimtab}
  v[0,0] := select(s[1,s],select(flip[1,sx], flip[1,sx], flip[1,sy]),flip[1,z]) \end{verbatimtab}
  We note that these examples are considered ``bad'' in \cite{XXX} since there
  no information about honest secrets should be revealed to the adversary in
  their threat model. For this reason they disallow reuse of flips through a
  linear type discipline, which is a culprit in both of these examples. However,
  as we have shown in Example \ref{example-otp} the reuse of flips is useful in
  the modeling of symmetric key encryption, and generally we will not enforce
  the same linear type discipline on the use of flips.
\end{example}

>>>>

Here we introduce some examples to illustrate $\minifed$ and how it
can be used to model secure communication protocols for values in the
binary field. Most of these are translations (into $\minifed$) of
object examples in previous related work \cite{XXX}. We will return to
these as running examples throughout the paper to illustrate various
concepts and advantages of our methods. In Section \ref{section-metalang}
we will formulate a larger example implementation of Yao's
Garbled Circuits (Example \ref{example-ygc}). 
\begin{example}[One-Time Pad]
  \label{example-otp}
As observed in \cite{XXX} and elsewhere, coin flips with $\exor$ can
be used to model one-time pad encryption in the binary field. On the
basis of this we can model secure communication between over an
insecure channel using symmetric key encryption. In the following
program, we assume $H = \{ 1,2 \}$ and $C = \{ 0 \}$. Client 1 first
shares the randomly generated ``key'' $\fx{1}{0}$ with client 2
through view $\view{2}{0}$. Then, client 1 encrypts its secret
$\sx{1}{0}$ and sends it to party 0, which relays the ciphertext in
$\vx{0}{0}$ to client 2. Finally, client 2 decrypts the the ciphertext
and stores the plaintext in $\vx{2}{2}$.
\begin{verbatimtab}
v[2,0] := f[1,0];
v[0,0] := f[1,0] xor s[1,0];
v[2,1] := v[0,0];
v[2,2] := v[2,1] xor v[2,0]
\end{verbatimtab}
Intuitively, this protocol is \emph{correct} because $\vx{2}{2}$ is
exactly correlated with the secret $\sx{1}{0}$, and it is
\emph{secure} because the corrupt view $\vx{0}{0}$ in isolation is
probabilistically independent of the secret $\sx{1}{0}$.
\end{example}

\begin{example}[$\lambda_{\mathrm{obliv}}$]
  \label{example-lambda-obliv}
  In \cite{XXX}, Figure 3, two examples are introduced that illustrate
  subtleties of probabilistic programming in
  $\lambda_{\mathrm{obliv}}$, a language for oblivious memory
  management. We consider their translations here where we
  assume $H = \{ 1 \}$ and $C = \{ 0 \}$. First, the following
  example shows that the reuse of coin flips can result in release of
  information, even though flips are chosen from a uniform
  distribution. This is because the adversary can deduce that
  $\secret{1}{s}$ is more likely to be 1 in case their views are the
  same value. We call this subexample $(a)$:
  \begin{verbatimtab}
    v[0,0] := select(s[1,s], flip[1,sx], flip[1,sy]);
    v[0,1] := flip[1,sx] \end{verbatimtab}
  In the next example, since the nested select is more likely to evaluate
  to $1$ than $0$, the adversary can deduce that $\secret{1}{s}$ is
  more likely to be 1 in case $\view{0}{0}$ is 1. We call this subexample $(b)$:
  \begin{verbatimtab}
  v[0,0] := select(s[1,s],select(flip[1,sx], flip[1,sx], flip[1,sy]),flip[1,z]) \end{verbatimtab}
  We note that these examples are considered ``bad'' in \cite{XXX} since there
  no information about honest secrets should be revealed to the adversary in
  their threat model. For this reason they disallow reuse of flips through a
  linear type discipline, which is a culprit in both of these examples. However,
  as we have shown in Example \ref{example-otp} the reuse of flips is useful in
  the modeling of symmetric key encryption, and generally we will not enforce
  the same linear type discipline on the use of flips.
\end{example}
